%
% File: thesisexample.tex   Version 1.8   May 6, 1999
%
% This is an example document for easychithesis, a 
% LaTeX2e style for formating theses at the University of
% Chicago.The easychithesis style was written by Bryan Clair and 
% Nathan Dunfield.  It contains detailed instructions for using
% easychithesis.
%
%  HINTS:
%
%  1. To get appendices, you don't do anything different from a normal
%     report document.  That means, put the command \appendix before
%     you begin your first appendix, then do each appendix with a
%     \chapter command.  Note that if you have only one appendix, it is
%     customary to leave it unnumbered.  Do this with \chapter*.
%
%  2.  If you use \chapter*, which produces unnumbered chapters, you 
%       have to add that chapter to the table of contents by hand, e.g.
%
%         \chapter*{Appendix}
%         \addcontentsline{toc}{chapter}{Appendix}
%
%  3.  If you get errors about
%   
%    Undefined control sequence.
%         \setspace@size ...rrsize \normalsize \@normalsize \else \@currsize \fi 
%
%     You need a newer version of the file ``setspace.sty''.
%
%  4.  Problems with math formulas in chapter headings:
% 
%         a.  Any lowercase letters in the formula are converted to
%         uppercase, e.g. f(x) becomes F(X).   If you really need
%         lowercase math letters in your chapter titles, use the
%         option plainchapterheads (and, if you want, type your
%         chapter titles in ALL CAPS so that the appearance doesn't
%         change).  Note there is no problem 
%         for section or subsection headings in either case.  (Options
%         such as plainchapterheads are given as part of the 
%         \documentclass command, see below under ``Document Options'').
%
%         b.  Some perfectly reasonable math commands when used in
%         \chapter give the error
%          ``LATEX ERROR: \command  ALLOWED ONLY IN MATH MODE.''
%         The solution to this is to do
%        
%              \newcommand{\mymath}{problem math goes here}
%       
%         and then
%        
%              \chapter{All about \protect\mymath}
%
%         also, the option plainchapterheads will fix this too.
%
%  5. If your References section doesn't show up in the table of
%     contents, you need to add the line \addcontentsline...
%     as done at end of this file.   Make sure that you include the 
%     page break command as done there or else you may end up
%     with the wrong page number in your table of contents. 

\documentclass{ucetd}
% Document Options: 
%
% Note if you want to save paper when printing drafts, replace the
% above line by
% 
%   \documentclass[singlespace]{easychithesis}
% 
% or 
% 
%   \documentclass[onehalfspace]{easychithesis}
%
% Also the ``double spacing'' provided by this style is not ``true''
% doublespacing as defined by setspace.sty.  Instead, it is the same
% as on the old LaTeX 2.09 thesis style ``chithesis''.  If you want 
% ``true'' doublespacing (if there is such a thing), give the option 
% truedoublespace.  The increase in tree murder will be on your 
% conscience, not mine.
%
%  Similarly, if you need to use the plainchapterheads option, you do
%   
%  \documentclass[plainchapterheads]{easychithesis}
%
% You can give more than one option, if you desire.
\usepackage{pdfpages}
\usepackage{csquotes}
\usepackage{nameref}
\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{changepage}
\usepackage{float}
\usepackage{caption}
\captionsetup{font={stretch=1}}
\usepackage{rotating}
\usepackage{subfigure,epsfig,amsfonts}
\usepackage{natbib}

\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{verbatim}   % useful for program listings
%\usepackage{color}      % use if color is used in text
%\usepackage{subfigure}  % use for side-by-side figures
%\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
\usepackage[numbered,framed]{docu/matlab-prettifier}

\let\ph\mlplaceholder % shorter macro
\lstMakeShortInline"

\lstset{
	style              = Matlab-editor,
	basicstyle         = \mlttfamily,
	escapechar         = ",
	mlshowsectionrules = true,
}
\begin{document}

% Create the official title
\title{Dynamic modulation of actomyosin contractility and cortical flow by actin filament recycling} 
\author{William McFadden}
\date{June 2017}
\department{Biophysical Sciences}
\degree{Doctor  of Philosophy} 

% \dedication : Use for a dedication, copyright, or epigraph.
%               Produces a page with no number for the text which follows
%               If you want centering, do it yourself with 
%               \begin{center} and \end{center}.  You can have more
%               than one `dedication'.
\dedication{ For Claire, you kept me going.}




 

%% Basic setup commands
% If you don't want a title page comment out the next line and uncomment the line after it:
\maketitle
%\omittitle

% These lines can be commented out to disable the copyright/dedication/epigraph pages
\makecopyright
\makededication


%% Make the various tables of contents
\tableofcontents
\listoffigures
\listoftables

\acknowledgments
I'd like to thank my advisor, Ed Munro, Birali Runesha, Francois Robin, Patrick McCall, Jon Michaux, Younan Li, Baixue Yao, Shiladitya Banerjee, the University of Chicago Biophysical Sciences program, Michele Wittels, Artifice, Pete Dahlberg, Adam Hammond, James Crooks, the uchicago myCHOICE program, the Insight Data Science Fellowship Program, Color Genomics, Robbie Sliwinski, my fiancee, Claire Stevenson, her family, David Stevenson and Marilyn Lucas, my brother, Andrew McFadden, and my mom, Deb McFadden.  Without all of these people and programs, I wouldn't have made it through this work and come out the other side with something of value.


\abstract
Actomyosin-based cortical flow is a fundamental engine for cellular morphogenesis.  Cortical flows are generated by cross-linked networks of actin filaments and myosin motors, in which active stress produced by motor activity is opposed by passive resistance to network deformation.  Continuous flow requires local remodeling through crosslink unbinding and/or filament disassembly. But how local remodeling tunes stress production and dissipation, and how this in turn shapes long range flow, remains poorly understood. To address this question, I developed a computational model for cross-linked actomyosin networks based on minimal requirements for production and dissipation of contractile stress, namely asymmetric filament compliance, spatial heterogeneity of motor activity, reversible cross-links and filament turnover.  Using this model, I characterized systematically how the production and dissipation of network stress each depend on network architecture, cross-link dynamics and filament turnover.  Then I determined how these dependencies combine to determine overall rates of cortical flow. My analysis predicts that filament turnover plays two key roles in shaping cortical flow: First, it allows networks to maintain active stress at steady state against external resistance and second,  it allows networks to continuously dissipate passive internal resistance to external force, while maintaining structural integrity. My model predicts that steady state stress increases with filament lifetime up to a characteristic time $\tau_{a}$, then decreases with lifetime above $\tau_{a}$; Effective viscosity increases with filament lifetime up to a characteristic time $\tau_c$, and then becomes independent of filament lifetime and sharply dependent on crosslink dynamics.  Finally, I show that these individual dependencies of active stress and effective viscosity define multiple regimes of steady state flow.  In particular my model predicts the existence of a regime, where filament lifetimes are shorter than both $\tau_c$ and $\tau_{a}$, in which dependencies of effective viscosity and steady state stress cancel one another, such that flow speed is insensitive to filament turnover.  My model also predicts a simple dependence of flow velocity on molecular scale properties of motor activity and crosslink dynamics.  In complementary work, in collaboration with other members of the Munro Lab, I developed methods to measure actin filament turnover in C. elegans embryos using single molecule imaging. Together, these results provide a framework for understanding how animal cells tune cortical flow through local control of network remodeling.  

\mainmatter

%
% Body Chapters
%
\chapter{Introduction}
\input{introduction/introduction}

\chapter{Single molecule measurements of actin filament turnover}
\input{nmeth/nmeth}

\chapter{Filament Recycling and Sustained Contractile Flows in an Actomyosin Network}
\label{sec:core}
\input{active/active}
\input{active/activesup}

\chapter{A model of upstream actomyosin regulators in pulsed contractions}
\input{pulse/pulse_paper}

\chapter{Conclusions, Open Issues, \& Future Directions}
\input{future/future}

\appendix

\chapter{Phases of deformation in filament networks with cross-link slip}
\label{chap:slippage}
\input{slippage/slippage}

\chapter{Additional information on pulse model}
\label{chap:morepulse}
\input{pulse/pulse}

\chapter{Reducing power consumption in High Performance Computing}
\input{edeals/datacenter_energy}

\chapter{Source Code and Documentation}
\input{docu/docu}
\input{model/explanation}

\chapter{Artistic Interpretations of filament recycling}
\input{art/art}

\chapter{Workshop on modeling in biology}
\input{workshop/workshop}


%
% References (the thesis office prefers that to Bibliography...)
%
% They also prefer that it be single spaced.
% The pagebreak command is necessary inorder to insure that 
%  the page number that appears in the table of contents is
%  the correct one.   
\makebibliography



\end{document}